---
title: "Test parse Maria"
output: html_document
---

Redefining functions. 

```{r}
library(readr)

good_lines <- function(x) {
  grep("^\\{\"created.*ms\":\"\\d+\"\\}$", x, value = TRUE)
}
good_lines2 <- function(x) {
  x <- x[nchar(x) > 0]
  print(length(x))
  x <- grep("{\"delete", x, fixed = TRUE, invert = TRUE, value = TRUE, perl =TRUE)
  x <- grep("{\"limit", x, fixed = TRUE, invert = TRUE, value = TRUE, perl = TRUE)
  co <- grep("\\d+\"\\}$", x, invert = TRUE, perl = TRUE)
  print(length(x))
  print(length(co))
  if (length(co) > 0) {
    for (i in seq_along(co)) {
      if (co[i] + 1 > length(x)) break
      x[co[i]] <- paste0(x[co[i]], x[co[i] + 1])
    }
    x <- x[-c(co + 1)]
    while (!grepl("\\d+\"\\}$", x[length(x)])) {
      x <- x[-length(x)]
      if (length(x) == 0) break
    }
  }
  x
}

parse_stream2 <- function(file_name, ...) {
  if (!identical(getOption("encoding"), "UTF-8")) {
    op <- getOption("encoding")
    options(encoding = "UTF-8")
    on.exit(options(encoding = op), add = TRUE)
  }
  print('stage1')
  s <- tryCatch(jsonlite::stream_in(file(file_name), ...), error = function(e)
    return(NULL))
  print(s)
  if (is.null(s)) {
    print('stage2')
    d <- readr::read_lines(file_name, skip_empty_rows = TRUE,)
    print(length(d))
    if (length(d) > 0) {
      tmp <- tempfile()
      on.exit(file.remove(tmp), add = TRUE)
      d <- good_lines2(d)
    }
    print('stage3')
    print(length(d))
    if (length(d) > 0) {
      dd <- sapply(d, function(x) {
        o <- tryCatch(jsonlite::fromJSON(x),
          error = function(e) return(FALSE))
        if (identical(o, FALSE)) return(FALSE)
        return(TRUE)
      }, USE.NAMES = FALSE)
      writeLines(d[dd], tmp)
      print('stage4')
      s <- jsonlite::stream_in(file(tmp, "rb"))
    }
  }
  print('stage5')
  if (length(s) == 0L) s <- NULL
  print(s)
  print('stage6')
  tweets_with_users(s)
}

```

What happens when you run this function? I usually get to `stage4` before it throws an error
```{r}

parse_stream2('streamed_tweets.json')



```
```{r}

print(default_locale())

d <- read_lines(
  'streamed_tweets.json',
  skip = 0,
  skip_empty_rows = TRUE,
  n_max = Inf,
  locale = default_locale(),
  na = character(),
  lazy = TRUE,
  num_threads = readr_threads()
)
print(length(d))
print(d[1:5])
```
There's some discrepancy between our read_lines function, perhaps due to some encoding defaults? My output of the above cell is:

<locale>
Numbers:  123,456.78
Formats:  %AD / %AT
Timezone: UTC
Encoding: UTF-8
<date_names>
Days:   Sunday (Sun), Monday (Mon), Tuesday (Tue), Wednesday (Wed), Thursday (Thu), Friday (Fri), Saturday (Sat)
Months: January (Jan), February (Feb), March (Mar), April (Apr), May (May), June (Jun), July (Jul), August (Aug), September (Sep), October (Oct),
        November (Nov), December (Dec)
AM/PM:  AM/PM
[1] 3473
[1] "{\"delete\":{\"status\":{\"id\":1453782957320138756,\"id_str\":\"1453782957320138756\",\"user_id\":1237756326836498433,\"user_id_str\":\"1237756326836498433\"},\"timestamp_ms\":\"1635845265520\"}}"
[2] ""                                                                                                                                                                                                    
[3] "\n{\"delete\":{\"status\":{\"id\":1455466634840268816,\"id_str\":\"1455466634840268816\",\"user_id\":895242923666796544,\"user_id_str\":\"895242923666796544\"},\"timestamp_ms\":\"1635845265611\"}}"
[4] ""                                                                                                                                                                                                    
[5] "\n"  
